---
title: "Project 1: Frequent k-mers in the SARS-CoV-2 genome"
author: "Jason Weston, Raghda Kailany, Calicia Perea"
due date: "2023-02-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Abstract:
  In this document, we will discuss multiple different questions pertaining to the SARS-CoV-2 genome. Tasks 1 and 2 will 
  go over the different methods of computationally discovering frequent k-mer patterns. The algorithims of counting these
  patterns will be implemented through the FrequentWords() and BetterFrequentWords() approaches. Task 3 will allow us to 
  generate random DNA sequences of various lengths using r-markdown. Task 4 will provide graphs for the runtimes of the
  algorithims implemented in Task 1 and 2, which will be compared. Task 5 will use our algorithims to report the most
  frequent k-mers of varrying sizes in the coronavirus 2 genome. Finally, Task 6 will allow us to determine which genes 
  certain k-mers belong to and whether or not they are in an intergeneic region. 

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
